\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-05-03 Review-response.tex

\documentclass[11pt,twoside]{article}
% \usepackage{subfigure}
% \usepackage{latexsym}
% \usepackage{graphicx}

% \usepackage{floatflt}
% \usepackage{float}

\input{preamble}

\renewcommand{\baselinestretch}{0.973}

\begin{document}
\thispagestyle{empty}
\pagestyle{empty}
\setlength{\parindent}{0pt} 
\setlength{\parskip}{2ex}

Kanna Rajan\\
Principal Researcher for Autonomy\\
Monterey Bay Aquarium Research Institute (MBARI)\\
Moss Landing, California\\
http://www.mbari.org/staff/kanna/\\
http://www.mbari.org/autonomy/index.htm \\
(831) 775-1833 (Work)\\

Reviewer and Editor for the manuscript \textsf{\underline{Towards Deliberative Control in Marine Robotics}}\\

Dear Mae,

First and foremost, we would like to thank the reviewer of our
manuscript above for the extensive and valuable comments provided. And
we thank you for your efforts to pull this all together.

We are heartened by the reviewers comments that the manuscript
``follows the intent and spirit'' of the book's theme. And we are
delighted in her/his belief that the manuscript should be accepted for
publication.

We have \emph{carefully} gone over all the comments provided. The
attached revised manuscript reflects those questions/comments from the
review and are highlighted in \kcomment{red} . In a number of
instances, we have taken the liberty to tighten the text for the
English and in one instance added some suplemental material which is
substantial, to explain how the \eu planner components work. We have
also added a couple of figures to better illustrate the concepts per
the reviewer's suggestions. The changes in sum are \underline{not}
substantial given the feedback. And as you would likely see, we've
worked hard to address all the comments while keeping the material
accessible.

Thank you once again for all your efforts on our collective behalf for
this book. We look forward to working with you to bring the book out
for educators at the earliest.

\vspace{+2cm}
\begin{tabbing}
\hspace{+10cm}\=Kanna Rajan\\
\>Corresponding Author\\
\end{tabbing}

\end{document}
\end{input}

### 2012-05-03 europa-basics.tex
updates

\rx is an adaptive, artificial intelligence based controller and
provides general framework for building reasoning systems for
real-world autonomous vehicles. At MBARI \rx is used for AUV control;
another instantiation of the system is being used for control of a
terrestrial personal robot \cite{pr2, Meeussen:2010dn}. The
development of \rx has been targeted at surveying a number of
oceanographic features which are dynamic and spatio-temporally
unpredictable. Typically this requires our AUVs to balance the goals
of coverage spatially while opportunistically following features of
scientific interest and to do so while being aware of its own
limitations in terms of resources (\eg the battery state of charge)
and overall proximity to other observational assets for obtaining
scientific ground-truth. We are interested in representational
frameworks that allow robots to pursue long-term objectives while
choosing short-term gain and can gracefully deal with exogenous or
endogenous change.

To enable this responsiveness to external observations, the agent has
to be able to synthesize plans insitu and to re-plan without human
intervention. To do so we use a temporal constraint-based planner with
a demonstrated legacy of having flown on NASA space missions. Our
autonomy architecture brings three key innovations for AUV control:
in-situ plan synthesis, the use of flexible plan representations with
a sound theoretical basis and systematic compositional control with
the use of partitioned networks doing so with a demonstrated
capability at sea in novel ocean observation methods.

The next few sections will cover \eu in a bottom-up fashion, going
from the generic theoretical framework that underlies \eue, to the
specific representation, modeling and algorithms implemented by it.  A
brief introduction to Constraint Programming and Constraint-Based
Planning is provided followed by the specific representation that \eu
uses to undertake Constraint-Based Planning.  Subsequently, we provide
an overview of \eus architecture and how it can be embedded in a
planning application such as \rxe. Finally, \eus modeling, inference
and search mechanisms are covered in detail so that the reader can
understand how \rx can perform deliberative planning and react to
execution events by embedding and customizing \eu.

@@

\begin{figure}[b]
\centering
  \includegraphics[scale=0.35]{figs/shopping_europa.pdf}
  \caption{\small A potential plan for a robot shopping for groceries.}
\label{fig:shop:shopping}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.3]{figs/Example-NQueens1.jpg}
\caption{\small An $N$-Queens solution generated by \eu}
\label{fig:nqueens-2}
\end{figure}

\paragraph{} \textit{Scheduling}: In the Resource Constrained Project
Scheduling Problem (\texttt{RCPSP}) \cite{Bruckera99}, a project
consisting of a set of activities must be scheduled in a way that
satisfies minimum and/or maximum temporal separation constraints. The
activity schedule must also respect fixed limits on the availability
of resources required to perform each activity. In addition to
satisfying temporal and resource constraints, it is common for the
user to want to minimize makespan \cite{ghallab04} so that the entire
project is finished as early as possible. Fig. \ref{fig:rcpsp-1} shows
an example of a a solution provided by \eu for an \texttt{RCPSP}
instance with 10 activities, 5 resources and 30 temporal constraints.

\begin{figure}
\centering
\includegraphics[scale=0.25]{figs/Example-UBO0.jpg}
\caption{\small A \eu solution to an \texttt{RCPSP} \cite{Bruckera99}
  problem.}
\label{fig:rcpsp-1}
\end{figure}

\paragraph{} \textit{Planning}: The Shopping Agent Problem
\cite{russelnorvig} is a variation of the problem with which we
started this chapter.  In this problem, an agent needs to purchase a
set of products (milk, drill, etc) that are available at specific
locations (supermarket, hardware store, etc). The agent is subject to
temporal (must complete tasks by specific deadlines) and resource
(fuel, carrying capacity, etc) constraints and it needs to synthesize
actions that need to be performed to find and acquire the required
items, as well as when to perform each of those actions.
Fig. \ref{fig:shopping-1} shows a solution produced by \eu for such a
problem instance.

\begin{figure}
\centering
\includegraphics[scale=0.3]{figs/Example-Shopping0.jpg}
\caption{\small A \eu solution to a shopping agent problem domain where
  the agent needs to buy Bananas, Milk and a Drill.}
\label{fig:shopping-1}
\end{figure}

@@

Constraint Satisfaction Programming (also known as Constraint
Programming or \textsf{CP}) is a discipline that provides a generic
framework for representing, solving and making logical inference on
constraints. A complete treatment of this discipline is given in
\cite{marriott98,apt03} with concise introductions provided in
\cite{bartak99,lustig01}.

A constraint programming problem consists of a set of variables $V=
{x_1,..,x_N}$, where each variable takes values from a domain
$d_1,..,d_N$; in this chapter we will deal only with discrete and
finite domains. Given a defined conjunctive set of constraints on the
variables: $C=\{c_1(x_1,..,x_N), ..., c_K(x_1,..,x_N)\}$, the
objective is to find one or more value assignments to $V$ where all
constraints are satisfied. To solve a problem, \textsf{CP} techniques
use logical inference to perform Constraint Propagation, which
consists of two operations:

@@

To generate plans, the \texttt{CAIP} framework uses a plan-space search
approach \cite{ghallab04}, where a partial plan is evolved until all
open goals are achieved, and all inconsistencies are removed. The
specific search algorithm used by \eu will be covered in detail below.

>>>>

\rx is an adaptive, artificial intelligence based controller and
provides \kcomment{a} general framework for building reasoning systems
for real-world autonomous vehicles. At MBARI \rx is used for AUV
control; another instantiation of the system is being used for control
of a terrestrial personal robot \cite{pr2, Meeussen:2010dn}. The
development of \rx has been targeted at surveying a number of
oceanographic features which are dynamic and spatio-temporally
unpredictable. Typically this requires our AUVs to balance the goals
of spatial coverage while opportunistically following features of
scientific interest and to do so while being aware of its own resource
limitations (\eg the battery state of charge) and overall proximity to
other observational assets for obtaining scientific ground-truth. We
are interested in representational frameworks that allow robots to
pursue long-term objectives while choosing short-term gain and can
gracefully deal with exogenous or endogenous change.

To enable this responsiveness to external observations, the agent has
to be able to synthesize plans insitu and to re-plan without human
intervention. \rx uses a temporal constraint-based planner with a
demonstrated legacy of having flown on NASA space missions. Our
autonomy architecture brings three key innovations for AUV control:
in-situ plan synthesis, the use of flexible plan representations with
a sound theoretical basis and systematic compositional control with
the use of partitioned networks and doing so with a demonstrated
capability at sea \kcomment{for} novel ocean observation methods.

The next few sections will cover \eu in a bottom-up fashion, going
from its \kcomment{general} theoretical framework, to the specific
representation, modeling and algorithms implemented by it.  A brief
introduction to Constraint Programming and Constraint-Based Planning
is provided followed by the specific representation that \eu uses to
undertake Constraint-Based Planning.  Subsequently, we provide an
overview of \eus architecture and how it can be embedded in a planning
application such as \rxe. Finally, \eus modeling, inference and search
mechanisms are covered in detail so that the reader can
\kcomment{appreciate} how \rx can perform \kcomment{deliberation while
  being responsive to events in the real-world}.

@@

Planning as an activity is ingrained in human decision-making
\cite{berthoz} and its generalization into a computational framework
demonstrating machine intelligence \kcomment{has for long been}
targeted by pioneers in computer science
\cite{computersthought}. Early work in this context focused on logical
theorem proving by computer \cite{green69} which has formed the basis
of much of the discipline. The emphasis in these early efforts was to
logically derive the existence proof of a trajectory of actions for a
hypothetical robot (moving blocks, chess pieces, furniture etc) to
achieve a specific goal given specific initial conditions. Two
important properties of \emph{Soundness}\footnote{A planning algorithm
  is sound if invoked on a problem $P$ returns a plan which is a
  solution for $P$.} and \emph{Completeness}\footnote{A planning
  algorithm is complete if invoked on a solvable problem $P$ is
  guaranteed to return a solution.} along with derived results for
algorithmic complexity \cite{gareyjohnson,corman} were a defining
cornerstone for understanding how different computational paradigms
could actually be tractable first in simulation and subsequently in
actual robotic platforms. In this chapter our emphasis is to focus on
embedded AI Planning and the execution of plans on an embedded
\kcomment{marine robotic} platform. The techniques we highlight are
general purpose as noted in Section \ref{sec:intro}.

\begin{figure}[b]
\centering
  \includegraphics[scale=0.45]{figs/shopping_europa.pdf}
  \caption{\small A potential plan for a robot shopping for groceries.}
\label{fig:shop:shopping}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.3]{figs/Example-NQueens1.jpg}
\caption{\small An $N$-Queens solution generated by \eue.}
\label{fig:nqueens-2}
\end{figure}

\paragraph{} \textit{Scheduling}: The Resource Constrained Project
Scheduling Problem (\texttt{RCPSP}) \cite{Bruckera99}, consists of a
set of activities that must be scheduled in a way that satisfies
minimum and/or maximum temporal separation constraints. The activity
schedule must also respect fixed limits on the availability of
resources required to perform each activity. In addition to satisfying
temporal and resource constraints, it is common for the user to want
to minimize makespan \cite{ghallab04} so that the entire project is
finished as early as possible. Fig. \ref{fig:rcpsp-1} shows an example
of a a solution provided by \eu for an \texttt{RCPSP} instance with
$10$ activities, $5$ resources and $30$ temporal constraints.

\begin{figure}[t]
\centering
\subfloat[\small A \eu solution to an \texttt{RCPSP} \cite{Bruckera99}
  problem.]{\label{fig:rcpsp-1}\includegraphics[scale=0.25]{figs/Example-UBO0.jpg}}\qquad
\subfloat[\small A \eu solution to a shopping agent problem domain where
  the agent needs to buy Bananas, Milk and a Drill.]{\label{fig:shopping-1}\includegraphics[scale=0.3]{figs/Example-Shopping0.jpg}}
\caption{\small \eu based solutions to scheduling and planning problems.}
\end{figure}

\paragraph{} \textit{Planning}: The Shopping Agent Problem
\cite{russelnorvig} is a variation of the problem with which we
started this chapter.  An agent needs to purchase a set of products
(milk, drill, etc) that are available at specific locations
(supermarket, hardware store, etc). The agent is subject to temporal
(must complete tasks by specific deadlines) and resource (fuel,
carrying capacity, etc) constraints and it needs to synthesize actions
that need to be performed to find and acquire the required items, as
well as when to perform each of those actions.
Fig. \ref{fig:shopping-1} shows a solution produced by \eu for such a
problem instance.

@@

Constraint Satisfaction Programming (also known as Constraint
Programming or \textsf{CP}) is \kcomment{an AI} discipline that
provides a generic framework for representing, solving and making
logical inference on constraints. A complete treatment of this
discipline is given in \cite{marriott98,apt03} with concise
introductions provided in \cite{bartak99,lustig01}.

A constraint programming problem consists of a set of variables $V=
{x_1,..,x_N}$, where each variable takes values from a domain
$d_1,..,d_N$; in this chapter we will deal only with discrete and
finite domains. Given a defined conjunctive set of constraints
\kcomment{\cite{gen87}} on the variables: $C=\{c_1(x_1,..,x_N), ...,
c_K(x_1,..,x_N)\}$, the objective is to find one or more value
assignments to $V$ where all constraints are satisfied. To solve a
problem, \textsf{CP} techniques use logical inference to perform
Constraint Propagation, which consists of two operations:

@@

To generate plans, the \texttt{CAIP} framework uses a plan-space
search approach \cite{ghallab04}, where a \emph{partial
  plan}\footnote{\kcomment{A partial plan is a subsequence of a plan
    which can be refined into a plan structure.}} is evolved until all
open goals are achieved and all inconsistencies are removed. The
specific search algorithm used by \eu will be covered in
\kcomment{further} detail below.
